---
title: "The Basics of highlightHTML"
author: "Brandon LeBeau"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Have you ever wanted to include some form of highlighting, either conditional or nonconditional, to a html document? If so, this package may be worthwhile to you. The `highlightHTML` package inject CSS into the HTML document automatically via ids (more information on CSS ids here: <http://www.cssbasics.com/css-ids/>). 

# Basic Example
Suppose you have a table like the following:

| Color Name | Number       |
|----------- | ------------ |
| Blue       |  5           |
| Green      |  35          |
| Orange     |  100         |
| Red        |  200         |

You could then add some conditional formatting by adding the following tags to the table.

| Color Name | Number       |
|----------- | ------------ |
| Blue       |  5  #bgblue  |
| Green      |  35          |
| Orange     |  100         |
| Red        |  200 #bgred  |

The addition of the *#bgblue* and *#bgred* indicates which cells will be changed. After turning the markdown document into an html file, this package can now be used to post-process the html file. The post-processing will add an id value for each cell with the *#bgblue* or *#bgred* and remove those from the table. 

The function to use for the post-processing is `highlight_html` and requires three arguments, the input file, the output file, and the CSS tags themselves. This will look something like the following using an example file from the package:

```{r function, eval=FALSE}
library(hightlightHTML)
file <- system.file('examples', 'bgtable.html', 
                    package = 'highlightHTML')
tags <- c("#bgred {background-color: #FF0000;}", 
  "#bgblue {background-color: #0000FF;}")
highlight_html(input = file, 
               output = tempfile(fileext = ".html"), 
               tags = tags,
               update_css = TRUE, 
               browse = TRUE,
               print = FALSE)
```

In the above `highlight_html` function call, the input file is saved to a temporary file. The `update_css` argument will inject the tags into the html document within any style tags that are found within the document. The `browse` argument will open the resulting post-processed file in the default browser to be viewed directly. Finally, the `print` argument if TRUE, will print the html output to the R console. This may be useful for verification of potential errors in the post-processing.

## Formatting tables directly from R
There is also a function that helps facilitate the formatting of R tables with conditional formating called `table_id_inject`.

# Formatting Text
Formatting text is also simple in a markdown document. Braces `{}` are used to single text that should be formatted. Then, the addition of an id tag to link this to the CSS formatting. 

For example, perhaps there is {#colgold some text} to turn gold. In the following example, the text "some text" would be processed to turn into gold using the CSS id #colgold. Another example file can be run with the following commands:
```{r text, eval = FALSE}
file <- system.file('examples', 'bgtext.html', package = 'highlightHTML')

# Change background color and text color with CSS
tags <- c("#bgblack {background-color: black; color: white;}", 
  "#bgblue {background-color: #0000FF; color: white;}",
  "#colgreen {color: green;}")
  
# Post-process HTML file
highlight_html(input = file, output = tempfile(fileext = ".html"),
               tags = tags, update_css = TRUE, browse = TRUE)
```

The same argument calls are valid as discussed above when post-processing tables.

# From Markdown to HTML directly.

